How to compute the fusion product of MV cycles in type A

### 2021-03-29 draft.tex
joels latest changes some notational

\subsection{Groups}

% \acom{Add $G_1$}
\acom{TODO: Algebraic groups over rings, i.e.\ the meaning of $G(K)$. The affine space of $m\times m$ matrices which we denote $ M_m$. The first congruence subgroup $G_1$ and why we take $\Oinf$ points instead of $\CC[t]$ points as some of the lit does.}

@@

\subsection{Lattices}
\label{ss:lat}
We will use the lattice model, so it is useful to recall the following definition. Let $ R \subset K$ be two rings (usually, but not always, $K$ will be a field). 
% \acom{When is $K$ not a field?}). Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and; e.g. K = C[t,t^{-1}] is not a field!!! 
Consider $ K^m $ as a $K$-module. By restriction $ K^m$ can be viewed as an $R$-module.  An $R$-lattice in $K^m$ 
% \acom{what is $M$? should be $K^m$?}; bc Joel was thinking about arbitrary free modules 
is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.  Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$. 
% 
\begin{comment}
\jcom{Maybe need that both $K$ and $R$ are integral domains and have the same field of fractions?} 
\acom{Roger has proved that what is written is ok.}
\rcom{Here's my argument: If $L \subset K^m$ is a free rank $m$ $R$-module and $L \otimes K = K^m$, then it's clear we that $L$ is generated by $m$ generators $v_1,\dots,v_m$ over $R$. Since $L\otimes K = K^m$, these also generate $K^m$ over $K$. Then we have a surjective map $K^m \twoheadrightarrow K^m$ given by sending a basis of $K^m$ to the generators $v_1,\dots,v_m$. Since any surjective endomorphism of finite $K$-modules is injective, the $v_1,\dots,v_m$ form a basis. I think the only thing that is needed is that the rings are commutative.}
\jcom{Great.}
\end{comment}

% The trivial lattice is 
% No more: L_0(R) = 
$ R^m \subset K^m $ is called the standard lattice. 
% We will abuse notation and denote $L_0(R)$ simply $L_0$ in the hope that the ring $R$ will be understood from the context. 
The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
% the set of such lattices 
this set and $\GL_m(K)/\GL_m(R)$. 
\acom{For example, we will frequently make use of the lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$ given $\lambda\in P$. If $e_1,\dots,e_m$ denote the standard basis elements of 
% $L_0(\cO)$ then 
$\cO^m$ then 
$$ 
L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
$$}
% \acom{Maybe abuse notation and warn the reader.}
% \acom{is it clear that $\GL(R^m) \le \GL(K^m)$ is normal?} \jcom{It isn't normal and the quotient is not a group.}

@@

\subsection{Affine Grassmannians} %  actors
% To map thick Gr to C is to map a lattice to the points where it isn't trivialzable; doesn't make sense to ask for poles 
% G(C(t))/G(C[t]) for example lives over the Ran space, finitely many eigenvalues; positive part of thick contains this guy as image 
Set $\AA = \AA^1$ and let $V_0$ denote the trivial rank $ m $ vector bundle. \acom{Change $V_0$}

@@

\begin{itemize}
    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by \acom{Change $V_0$}
    $$
    % \Gr = 
    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_0^\times $} \right\} \,. 
    $$
    % where $V_0$ is the trivial rank $m$ vector bundle.
    % and $ D_0$ is the formal disc centered at $ 0 \in \PP$.

    We also have a lattice description 
    $$ 
    \Gr = \left\{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \right\}\,.
    $$
    We obtain the lattice from $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, V_0)$ using $ \varphi$.  On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.\emoji{clap} \acom{Change $V_0$}
    % 
    \item For any $ s \in \CC $, 
    % \acom{should it be $\AA$ instead of $\CC$} 
    the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by \acom{Change $V_0$}
    $$
    % \Gr_s = 
    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D^\times_s $} \right\}\,.
    $$
    % where $D_s$ is the formal disc centered at $s$ viewed as an element of $\PP$.
    % \acom{What about fixing the notation $V_0$ somewhere?}

    We also have a lattice description 
    $$ 
    \Gr_s = \left\{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \right\} \,. 
    $$   
    \item The thick affine Grassmannian $\Grth = G(\Kinf)/G(\CC[t])$. % \CC\xT[t^{-1}]
    It is described in modular terms by
    $$
        % \Grth = 
        % \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_\infty $ } \right\}\,. % (a disc centered at $ \infty$)
    $$
    % where $D_\infty$ denotes a disc centered at $ \infty$. 
    % \acom{What is the difference between ``a disc'' and ``the formal disc''} \jcom{No difference.}

@@

    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s\in\AA$ varying).
    It is described in modular terms by \acom{Change $V_0$}
    % {\small
    $$
    % \Grbd = 
    % \begin{aligned}
        \left\{ 
            (V,\varphi,s) : V\text{ is a rank $m$ vector bundle on }\PP, \varphi : V \xrightarrow{\sim} V_0 \text{ on } \PP \setminus \{0, s\}  
        \right\} 
    % \end{aligned}
    $$%}
    % 
    The fibre of $\Grbd \to \AA$ over $ s \in \AA $ will be denoted $ \Gr_{0,s} $ and is given by
    % \rcom{why do we have the $s\ne 0$ restriction here} \jcom{it would work when $ s = 0$, but it looks a bit strange there.}
    % 
    $$ 
    % \Gr_{0,s} = 
    G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,. % := \pi^{-1}(s) 
    $$
    % \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
    % \jcom{Yes, that is one reason.  But also, there was a comment of yours before in the file, saying that you sometimes got confused that one point was fixed at 0, so this is a good notation to remind us (and the reader).  For the same reason, maybe we should write $ \Gr_{0, \AA}$ instead of $ \Gr_\AA$.}
    % \acom{lol}

@@

\begin{enumerate}
    \item First there is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
    \item Second, we have a map from the two point BD affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $
    % $$ \Grbd \rightarrow \Grth $$ 
    which is given in modular terms by restricting the trivialization to $ D_\infty$.  It is given in group-theoretic terms on the fibre over $ s $ by the inclusion
    $$
    G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])\,. 
    $$
    % \acom{Permission to update notation and replace $\CC\xT[t^{-1}]$ by $\Kinf$ as per your suggestion Joel?}
    % \jcom{Permission granted!}
    % \acom{replaced}

@@

\subsection{The fusion construction}
The following construction will be very important in this paper.  Let $ X_1, X_2 \subset \Gr$ be two subschemes. Then using the isomorphism $ \Gr \cong \Gr_s $, for each $ s $, we obtain a subscheme $ X_1 \times X_2 \subset \Gr \times \Gr_s $.  
% <<<<<<< HEAD
% Via \ul{this} \acom{rather, the above? $L\mapsto (L(0),L(s))$} 
Next, using the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $, 
for each $ s \ne 0$,  
\rcom{Joel: usually written $\Gr_{0,\AA^\times} \cong \Gr \times \Gr_s \times \AA^\times$, cite MVi} 
we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
% =======
% Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
% >>>>>>> 5a15ce15b14109bab482282aa5657c9596f7892d

We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $ X_1 \times X_2 \times \AA^\times $ inside of $ \Grbd $.  
We use the projection $ \pi: \Grbd \rightarrow \AA $ to form $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) \subset \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.  
We regard $ X_1 \circ X_2$ as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $. 
% \acom{Repeat question: what is this iso? Roger says maybe it's in MV?}
% \jcom{Now answered above.}

@@

\subsection{Some subvarieties of affine Grassmannians}
Now fix effective dominant coweights $ \lambda_i,\mu_i \in P_{++}$ of size $N_i$ ($i=1,2$) and their sums $ \lambda = \lambda_1 + \lambda_2, \mu = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$. 
% Coweights define elements in the various affine Grassmannians which we consider. Warning: We will write only coset representatives for elements of the various Grassmannians; we hope that it is evident which right cosets they represent. 
% the right cosets which they represent are clear from the context.

\acom{At some point at least mention that we expect this to go through for permutations of $\mu_i\in P_{++}$ i.e.\ skew partitions? or non-dominant and non-negative coweights; so long as their sum $\mu_1 + \mu_2$ is effective dominant.}

The following subsets are indexed by coweights. 
% 
\begin{itemize}
    % \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
    % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
    % \item The lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$. 
    % $$ 
    % L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
    % $$ 
    % \acom{This definition makes sense for any $\lambda\in P$? Also, we don't really need it here---I have moved it up to the lattices section.}
    \item The orbit $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
    % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
    This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian. \acom{Do we need to justify this.}
    % 
    \item The family $ \overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0, \AA} = \overline{\Gr}^{\lambda_1} \ast_\AA \overline{\Gr}^{\lambda_2}$. 
    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda_1}\times\overline\Gr^{\lambda_2}\times\AA^\times}$..}
    %\acom{should we also subsript this family with $0,\AA$?}

    By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.  
    % By \cite[Proposition 3.1.14]{zhu2016introduction},
    % Zhu's theorem (\jcom{need ref} \acom{pretty sure it's }), 
    % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.
    Over $s=0$ the fibre is shown to be $ \overline{\Gr}^{\lambda_1 + \lambda_2}$ in the proof of \cite[Proposition 3.1.14]{zhu2016introduction}.

    Suppose that $ s \ne 0$.  In the fibre $\overline{\Gr}_{0,s}^{\lambda_1, \lambda_2}$ we have the open locus $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ coming from transporting $ \Gr^{\lambda_1} \times \Gr^{\lambda_2} $ via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $.  This open locus is a $ G(\CC[t])$-orbit
    % .  The lattice description of $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ 
    whose lattice description is given in \Cref{le:Grl1l2} below.
    % \acom{Why $G(\CC[t])$. Because we are on the left side!}

    \item The locus $\cW_\mu = G_1\xt[t^{-1}] t^\mu \subset \Grth $.  
    % 
    \acom{What goes wrong if we take $G_1[t^{-1}]t^\mu$ instead?} \jcom{Then it lives in the thin Grassmannian.  And unless $ A $ is nilpotent, then $g(A)$ won't live there.} \acom{But our $A$ is always nilpotent? Another notational thing is $G_1\xt[t^{-1}] = G_1(\CC\xt[t^{-1}])$ and in our paper this short hand is only used for these kernel subgroups.}
    In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.  The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below. 
    % \acom{que est-ce?} \jcom{It's not very relevant for this paper.  Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN--filtration; it is a partial flag of subbundles of type determined by $ \mu$.  We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.  Maybe ``preserves'' is not the best word above.}
    % A: Ok thanks!
    % 
    \item The semi-infinite orbit $ S^\mu = N(\cK)t^\mu \subset \Gr $.  
    \item The family of semi-infinite orbits $ S^{\mu_1, \mu_2}_{0,\AA} := S^{\mu_1} \ast_\AA S^{\mu_2}$.  If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
    $$
    % S^{\mu_1, \mu_2}_{0,s} = 
    N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
    $$
    % TODO: resolve
    % \jcom{Maybe we should introduce the $ L_{\mu_1, \mu_2} $ notation, but I'm not sure it is necessary.}
    On the other hand, if $ s = 0$, then the fibre $S^{\mu_1, \mu_2}_{0,0} $ equals $ S^{\mu_1 + \mu_2}$. 
    % TODO: resolve
    % \acom{changed $\mu$ to $\mu_1 + \mu_2$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} $}

    \jcom{These two statements here require some proof, so perhaps they should be split off as a lemma in ``Rising action''.}
    % TODO!

@@

\jcom{In this proof, I made some statements about $\mu$ dominant, which are incorrect (as Anne knows). To make them correct we should either switch to having $ \mu$ being antidominant or switch $ N$ to $ N_-$.  In this proof $ g(A)$ generally denotes a group element, rather than an affine Grassmannian element which conflicts a bit with earlier usage.}

>>>>

\subsection{Groups}
Let $H $ be an algebraic group over $ \CC $.  We will be interested $ H(R)$ where $ R $ is a $\CC$-algebra, for example $R = \CC[t], \cO_s$, etc.  Note that evaluation at $ t = s$ provides a group homomorphism $ H(\cO_s) \rightarrow H$.  We denote the kernel of this map by $ H_1(\cO_s)$.  We will be particularly interested in this construction in the case $ s = \infty$, which gives us the group $ H_1(\Oinf)$ which is often called the first congruence subgroup.
% \acom{Add $G_1$}
%\acom{TODO: Algebraic groups over rings, i.e.\ the meaning of $G(K)$. The affine space of $m\times m$ matrices which we denote $ M_m$. The first congruence subgroup $G_1$ and why we take $\Oinf$ points instead of $\CC[t]$ points as some of the lit does.}

@@

We will also be interested in the affine space $ M_m$ of $m$x$m$ matrices.  Note that for any $ \CC$-algebra $ R $,  $GL_m(R) $ consists of those matrices $ g \in M_m(R) $ whose determinant is invertible in $ R$.  Thus $ t^\lambda \in M_m(\CC[t])$ for all $ \lambda \in P_{++}$ but $ t^\lambda \in GL_m(\CC[t]) $ if and only if $ \lambda = 0 $.

\subsection{Lattices}
\label{ss:lat}
We will use the lattice model, so it is useful to recall the following definition. Let $ R \subset K$ be two $\CC$-algebras (usually, but not always, $K$ will be a field). 
% \acom{When is $K$ not a field?}). Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and; e.g. K = C[t,t^{-1}] is not a field!!! 
Consider $ K^m $ as a $K$-module. By restriction $ K^m$ can be viewed as an $R$-module.  An $R$-lattice in $K^m$ 
% \acom{what is $M$? should be $K^m$?}; bc Joel was thinking about arbitrary free modules 
is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.  Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$. 
% 
\begin{comment}
\jcom{Maybe need that both $K$ and $R$ are integral domains and have the same field of fractions?} 
\acom{Roger has proved that what is written is ok.}
\rcom{Here's my argument: If $L \subset K^m$ is a free rank $m$ $R$-module and $L \otimes K = K^m$, then it's clear we that $L$ is generated by $m$ generators $v_1,\dots,v_m$ over $R$. Since $L\otimes K = K^m$, these also generate $K^m$ over $K$. Then we have a surjective map $K^m \twoheadrightarrow K^m$ given by sending a basis of $K^m$ to the generators $v_1,\dots,v_m$. Since any surjective endomorphism of finite $K$-modules is injective, the $v_1,\dots,v_m$ form a basis. I think the only thing that is needed is that the rings are commutative.}
\jcom{Great.}
\end{comment}

% The trivial lattice is 
% No more: L_0(R) = 
$ R^m \subset K^m $ is called the standard lattice. 
% We will abuse notation and denote $L_0(R)$ simply $L_0$ in the hope that the ring $R$ will be understood from the context. 
The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
% the set of such lattices 
this set and $\GL_m(K)/\GL_m(R)$, since $ GL_m(R) $ is the stabilizer of the standard lattice. 
\acom{For example, we will frequently make use of the lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$ given $\lambda\in P$. If $e_1,\dots,e_m$ denote the standard basis elements of 
% $L_0(\cO)$ then 
$\cO^m$ then 
$$ 
L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
$$}
% \acom{Maybe abuse notation and warn the reader.}
% \acom{is it clear that $\GL(R^m) \le \GL(K^m)$ is normal?} \jcom{It isn't normal and the quotient is not a group.}

@@

\subsection{Affine Grassmannians} %  actors
% To map thick Gr to C is to map a lattice to the points where it isn't trivialzable; doesn't make sense to ask for poles 
% G(C(t))/G(C[t]) for example lives over the Ran space, finitely many eigenvalues; positive part of thick contains this guy as image 
Set $\AA = \AA^1$ and let $\Vtriv$ denote the trivial rank $ m $ vector bundle.

@@

\begin{itemize}
    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by %\acom{Change $V_0$}
    $$
    % \Gr = 
    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_0^\times $} \right\} \,. 
    $$
    % where $V_0$ is the trivial rank $m$ vector bundle.
    % and $ D_0$ is the formal disc centered at $ 0 \in \PP$.

    We also have a lattice description 
    $$ 
    \Gr = \left\{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \right\}\,.
    $$
    We obtain the lattice from $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, \Vtriv)$ using $ \varphi$.  On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.\emoji{clap} \acom{Change $V_0$}
    % 
    \item For any $ s \in \CC $, 
    % \acom{should it be $\AA$ instead of $\CC$} 
    the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by     $$
    % \Gr_s = 
    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D^\times_s $} \right\}\,.
    $$
    % where $D_s$ is the formal disc centered at $s$ viewed as an element of $\PP$.
    % \acom{What about fixing the notation $V_0$ somewhere?}

    We also have a lattice description 
    $$ 
    \Gr_s = \left\{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \right\} \,. 
    $$   
    \item The thick affine Grassmannian $\Grth = G(\Kinf)/G(\CC[t])$. % \CC\xT[t^{-1}]
    It is described in modular terms by
    $$
         \Grth = 
         \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_\infty $ } \right\}\,. % (a disc centered at $ \infty$)
    $$
    % where $D_\infty$ denotes a disc centered at $ \infty$. 
    % \acom{What is the difference between ``a disc'' and ``the formal disc''} \jcom{No difference.}

@@

    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s\in\AA$ varying).
    It is described in modular terms by \acom{Change $V_0$}
    % {\small
    $$
    % \Grbd = 
    % \begin{aligned}
        \left\{ 
            (V,\varphi,s) : V\text{ is a rank $m$ vector bundle on }\PP, \varphi : V \xrightarrow{\sim} \Vtriv \text{ on } \PP \setminus \{0, s\}  
        \right\} 
    % \end{aligned}
    $$%}
    % 
    The fibre of $\Grbd \to \AA$ over $ s \in \AA $ will be denoted $ \Gr_{0,s} $ and is given by
    % \rcom{why do we have the $s\ne 0$ restriction here} \jcom{it would work when $ s = 0$, but it looks a bit strange there.}
    % 
    $$ 
    % \Gr_{0,s} = 
    G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,. % := \pi^{-1}(s) 
    $$
    % \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
    % \jcom{Yes, that is one reason.  But also, there was a comment of yours before in the file, saying that you sometimes got confused that one point was fixed at 0, so this is a good notation to remind us (and the reader).  For the same reason, maybe we should write $ \Gr_{0, \AA}$ instead of $ \Gr_\AA$.}
    % \acom{lol}

@@

\begin{enumerate}
    \item There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
    \item We have a map from the two point BD affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $
    % $$ \Grbd \rightarrow \Grth $$ 
    which is given in modular terms by restricting the trivialization to $ D_\infty$.  It is given in group-theoretic terms on the fibre over $ s $ by the inclusion
    $$
    G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])\,. 
    $$
    % \acom{Permission to update notation and replace $\CC\xT[t^{-1}]$ by $\Kinf$ as per your suggestion Joel?}
    % \jcom{Permission granted!}
    % \acom{replaced}

@@

\subsection{The fusion construction}
The following construction will be very important in this paper.
First, we recall that we have an isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $, 
for each $ s \ne 0$.  In turn, we have the isomorphism $ \Gr_s \cong \Gr$.

Gluing these together, we obtain
$$
\tau : \Gr_{0, \CC^\times} \rightarrow \Gr \times \Gr_{\CC^\times} \rightarrow \Gr \times \Gr
$$
where the first morphism is an isomorphism and the second map uses $ \Gr_s \cong \Gr $ on each fibre.  (This $\tau$ matches the map $ \tau $ of \cite{mirkovicvilonen}, except that we are working over $ \{0 \} \times \CC^\times$ instead of the complement of the diagonal in $ \CC^2 $.)

Let $ X_1, X_2 \subset \Gr$ be two subschemes.
We define the subscheme $ \tau^{-1}(X_1 \times X_2) \subset \Gr_{0, \CC^\times} $.

\jcom{I changed this a bit in order to match Mirkovic-Vilonen better.}
% =======
% Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
% >>>>>>> 5a15ce15b14109bab482282aa5657c9596f7892d

We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ inside of $ \Grbd $.  
Next, we consider the projection $ \pi: \Grbd \rightarrow \AA $ and define $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) \subset \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.  
We regard $ X_1 \circ X_2$ as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.

By this construction, $X_1 \ast_{\AA} X_2 $ is a flat family over $\CC$ whose fibre away from $0$ is $X_1 \times X_2$ and whose fibre over $ 0$ is $ X_1 \circ X_2$.

% \acom{Repeat question: what is this iso? Roger says maybe it's in MV?}
% \jcom{Now answered above.}

@@

\subsection{Some subvarieties of affine Grassmannians}
Now fix effective dominant coweights $\lambda_1, \lambda_2 \in P_{++}$ of sizes $N_1, N_2$  and their sums $ \lambda = \lambda_1 + \lambda_2 $ of size $ N = N_1 + N_2$. 
% Coweights define elements in the various affine Grassmannians which we consider. Warning: We will write only coset representatives for elements of the various Grassmannians; we hope that it is evident which right cosets they represent. 
% the right cosets which they represent are clear from the context.
We consider the following subschemes of the affine Grassmannians.
% 
\begin{itemize}
    % \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
    % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
    % \item The lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$. 
    % $$ 
    % L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
    % $$ 
    % \acom{This definition makes sense for any $\lambda\in P$? Also, we don't really need it here---I have moved it up to the lattices section.}
    \item The orbit $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
    % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
    This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian. \acom{Do we need to justify this.}
    % 
    \item The family $ \overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0, \AA} = \overline{\Gr}^{\lambda_1} \ast_\AA \overline{\Gr}^{\lambda_2}$. 
    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda_1}\times\overline\Gr^{\lambda_2}\times\AA^\times}$..}
    %\acom{should we also subsript this family with $0,\AA$?}

    By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.  
    % By \cite[Proposition 3.1.14]{zhu2016introduction},
    % Zhu's theorem (\jcom{need ref} \acom{pretty sure it's }), 
    % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.
    Over $s=0$ the fibre is shown to be $ \overline{\Gr}^{\lambda_1 + \lambda_2}$ by a theorem of Zhu \cite[Proposition 3.1.14]{zhu2016introduction}.

    Suppose that $ s \ne 0$.  In the fibre $\overline{\Gr}_{0,s}^{\lambda_1, \lambda_2}$ we have the open locus $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ coming from transporting $ \Gr^{\lambda_1} \times \Gr^{\lambda_2} $ via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $.  This open locus is a $ G(\CC[t])$-orbit
    % .  The lattice description of $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ 
    whose lattice description is given in \Cref{le:Grl1l2} below.
    % \acom{Why $G(\CC[t])$. Because we are on the left side!}
\end{itemize}
Now fix two effective coweights $ \mu_1, \mu_2 \in \mathbb N^m$ such that $ \mu_i$ has size $ N_i$ and such that $ \mu_1 + \mu_2 $ is dominant.  Using $ \mu_1, \mu_2$, we define the following subschemes.

\begin{itemize}
    \item The locus $\cW_\mu = G_1(\Oinf) t^\mu \subset \Grth $.  
    % 
    In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.  The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below. 
    % \acom{que est-ce?} \jcom{It's not very relevant for this paper.  Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN--filtration; it is a partial flag of subbundles of type determined by $ \mu$.  We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.  Maybe ``preserves'' is not the best word above.}
    % A: Ok thanks!
    % 
    \item The semi-infinite orbit $ S^\mu = N_-(\cK)t^\mu \subset \Gr $.  
    \item The family of semi-infinite orbits $ S^{\mu_1, \mu_2}_{0,\AA} := S^{\mu_1} \ast_\AA S^{\mu_2}$.  If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
    $$
    % S^{\mu_1, \mu_2}_{0,s} = 
    N_-(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
    $$
    % TODO: resolve
    % \jcom{Maybe we should introduce the $ L_{\mu_1, \mu_2} $ notation, but I'm not sure it is necessary.}
    On the other hand, if $ s = 0$, then the fibre $S^{\mu_1, \mu_2}_{0,0} $ equals $ S^{\mu_1 + \mu_2}$. 
    % TODO: resolve
    % \acom{changed $\mu$ to $\mu_1 + \mu_2$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} $}

    \jcom{These two statements here require some proof, so perhaps they should be split off as a lemma in ``Rising action''.  I changed $ N$ to $ N_-$.}
    % TODO!

@@

%\jcom{In this proof, I made some statements about $\mu$ dominant, which are incorrect (as Anne knows). To make them correct we should either switch to having $ \mu$ being antidominant or switch $ N$ to $ N_-$.  In this proof $ g(A)$ generally denotes a group element, rather than an affine Grassmannian element which conflicts a bit with earlier usage.}
